File-based localization of numerical perturbations in data analysis pipelines

### 2020-09-10 paper.tex

We demonstrated the applicability of our approach by evaluating two of the
arguably most complex pipelines in neuroimaging. Technically, these
pipelines consist of a mix of tools assembled from different toolboxes
through a variety of scripts written in different languages. Our file-based
approach, notably enabled by \reprozip, was able to analyze these pipelines
without requiring their instrumentation, which saved a very substantial
technical effort. The assumptions made on the pipeline structure, related
to the absence of concurrent writes, were not violated in our analysis, and
are likely to not impede \toolname's applicability to the most common
neuroimaging pipelines.

>>>>

\revised{The target users of the \toolname tool are primarily pipeline developers and users who have 
technical skills for creating Docker containers and Boutiques JSON files.}
We demonstrated the applicability of our approach by evaluating two of the
arguably most complex pipelines in neuroimaging. Technically, these
pipelines consist of a mix of tools assembled from different toolboxes
through a variety of scripts written in different languages. Our file-based
approach, notably enabled by \reprozip, was able to analyze these pipelines
without requiring their instrumentation, which saved a very substantial
technical effort. The assumptions made on the pipeline structure, related
to the absence of concurrent writes, were not violated in our analysis, and
are likely to not impede \toolname's applicability to the most common
neuroimaging pipelines.
